\Title

### 2020-03-02 manuscript/manuscript.tex
Add best prediction parameters tables

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}
\input{parameters_ground_survey.tex}
\input{parameters_airborne_survey.tex}

@@

>>>>

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}
\input{parameters_ground_survey.tex}
\input{parameters_airborne_survey.tex}
\input{best_parameters_ground_survey.tex}
\input{best_parameters_airborne_survey.tex}

@@

\begin{table*}
    \centering
    \caption{
        Combination of parameters that produce the best prediction when
        gridding the synthetic ground survey with each source distribution.
        The score of each best prediction is also shown.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestGroundSourceBellowDataConstantDepthDepth
                   & \BestGroundBlockMedianSourcesConstantDepthDepth
                   & \BestGroundGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestGroundBlockMedianSourcesConstantDepthSpacing
                     & \BestGroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestGroundGridSourcesConstantDepthPad \\
        Damping & \BestGroundSourceBellowDataConstantDepthDamping
                & \BestGroundBlockMedianSourcesConstantDepthDamping
                & \BestGroundGridSourcesConstantDepthDamping \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBellowDataConstantDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestGroundGridSourcesConstantDepthScore} \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestGroundSourceBellowDataRelativeDepthDepth
                   & \BestGroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (m) & -
                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
                & \\
        Damping & \BestGroundSourceBellowDataRelativeDepthDamping
                & \BestGroundBlockMedianSourcesRelativeDepthDamping
                & \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBellowDataRelativeDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesRelativeDepthScore}
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestGroundSourceBellowDataVariableDepthDepth
                   & \BestGroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \BestGroundSourceBellowDataVariableDepthDepthFactor
                     & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \BestGroundSourceBellowDataVariableDepthKNearest
                  & \BestGroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (m) & -
                     & \BestGroundBlockMedianSourcesVariableDepthSpacing
                     & \\
        Damping & \BestGroundSourceBellowDataVariableDepthDamping
                & \BestGroundBlockMedianSourcesVariableDepthDamping
                &  \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBellowDataVariableDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesVariableDepthScore}
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Combination of parameters that produce the best prediction when
        gridding the synthetic airborne survey with each source distribution.
        The score of each best prediction is also shown.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestAirborneSourceBellowDataConstantDepthDepth
                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
                   & \BestAirborneGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                     & \BestAirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestAirborneGridSourcesConstantDepthPad \\
        Damping & \BestAirborneSourceBellowDataConstantDepthDamping
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping \\
        R$^2$ score & \BestAirborneSourceBellowDataConstantDepthScore
                    & \BestAirborneBlockMedianSourcesConstantDepthScore
                    & \BestAirborneGridSourcesConstantDepthScore \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBellowDataConstantDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestAirborneSourceBellowDataRelativeDepthDepth
                   & \BestAirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (m) & -
                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
                & \\
        Damping & \BestAirborneSourceBellowDataRelativeDepthDamping
                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
                & \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBellowDataRelativeDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesRelativeDepthScore}
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestAirborneSourceBellowDataVariableDepthDepth
                   & \BestAirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \BestAirborneSourceBellowDataVariableDepthDepthFactor
                     & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \BestAirborneSourceBellowDataVariableDepthKNearest
                  & \BestAirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
        Damping & \BestAirborneSourceBellowDataVariableDepthDamping
                & \BestAirborneBlockMedianSourcesVariableDepthDamping
                &  \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBellowDataVariableDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesVariableDepthScore}
                & \\
    \end{tabular}
\end{table*}
